SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-05 related.tex
Machine Learning for Prefetching still needs work!

Spatial prefetchers include such well-understood examples as the next-line (or
next-$n$-line) prefetcher, and the stream prefetcher, and are distinguished by prefetching
data without regard for the order in which the data will be accessed.
In addition to simpler these, Somogyi \textit{et al.} 
propose Spatial Memory Streaming (SMS)~\cite{SMS}.  SMS works by learning
the spatial footprint of all data used by a program within a region of memory,
and when that region is revisited by the program, the same spatial footprint
is prefetched.  Ishii \textit{et al.} propose the Access Map Pattern Matching 
prefetcher (AMPM)~\cite{AMPM}, which creates a map of all accessed lines within a region
of memory, and then analyzes this map on every access to see if any 
fixed-stride pattern can be identified and prefetched that is centered on 
the current access. Pugsley \textit{et al.} propose the Sandbox Prefetcher~\cite{sandbox},
which analyzes candidate fixed-offset prefetchers in a sandboxed environment
to determine which is most suitable for the current program phase.  Michaud
proposes the Best-Offset Prefetcher~\cite{BOP}, which determines the optimal
offset to prefetch while considering memory latency and prefetch timeliness.

@@

A low-accuracy aggressive prefetcher can significantly harm performance.  To
minimize interference from prefetching, Wu \textit{et al.} propose
PACMan~\cite{pacman}, a prefetch-aware cache management policy.  PACMan
dedicates some LLC sets to each of three competing policies that treat demand
and prefetch requests differently, using the policy in the rest of the cache that shows the fewest
misses. Seshadri \textit{et al.} propose ICP~\cite{icp}, which
demotes a prefetch to the lowest reuse priority on a demand hit, based on the
observation that most prefetches are dead after their first hit.  To address
prefetcher-caused cache pollution, it also uses a variation of EAF~\cite{eaf}
to track prefetching accuracy, and inserts only accurate prefetches to the
higher priority position in the LRU stack.  Jain \textit{et al.} propose
Harmony~\cite{HarmonyHawkeye} to accomodate prefetches in their MIN 
algorithm-inspired Hawkeye cache management system.

>>>>

Spatial prefetchers include such well-understood examples as the next-line (or
next-$n$-line) prefetcher, and the stream prefetcher, and are distinguished by prefetching
data without regard for the order in which the data will be accessed.
In addition to simpler these, Somogyi \textit{et al.} 
propose Spatial Memory Streaming (SMS)~\cite{SMS}.  SMS works by learning
the spatial footprint of all data used by a program within a region of memory,
and when that region is revisited by the program, the same spatial footprint
is prefetched.  Ishii \textit{et al.} propose the Access Map Pattern Matching 
prefetcher (AMPM)~\cite{AMPM}, which creates a map of all accessed lines within a region
of memory, and then analyzes this map on every access to see if any 
fixed-stride pattern can be identified and prefetched that is centered on 
the current access. Pugsley \textit{et al.} propose the Sandbox Prefetcher~\cite{Sandbox},
which analyzes candidate fixed-offset prefetchers in a sandboxed environment
to determine which is most suitable for the current program phase.  Michaud
proposes the Best-Offset Prefetcher~\cite{BOP}, which determines the optimal
offset to prefetch while considering memory latency and prefetch timeliness.

@@

A low-accuracy aggressive prefetcher can significantly harm performance.  To
minimize interference from prefetching, Wu \textit{et al.} propose
PACMan~\cite{pacman}, a prefetch-aware cache management policy.  PACMan
dedicates some LLC sets to each of three competing policies that treat demand
and prefetch requests differently, using the policy in the rest of the cache that shows the fewest
misses. Seshadri \textit{et al.} propose ICP~\cite{icp}, which
demotes a prefetch to the lowest reuse priority on a demand hit, based on the
observation that most prefetches are dead after their first hit.  To address
prefetcher-caused cache pollution, it also uses a variation of EAF~\cite{eaf}
to track prefetching accuracy, and inserts only accurate prefetches to the
higher priority position in the LRU stack.  Jain \textit{et al.} propose
Harmony~\cite{Harmony} to accomodate prefetches in their MIN 
algorithm-inspired Hawkeye cache management system.
